# Data Collection

```{r, eval = TRUE, echo = FALSE}
suppressWarnings(library(knitr))

options(max.print = "200")
opts_chunk$set(echo = TRUE,
	             cache = FALSE,
               prompt = FALSE,
               tidy = FALSE,
               comment = NA,
               message = FALSE,
               warning = FALSE)
opts_knit$set(width = 80)

tableStyle <- function(t,
                       boot_opt = c("striped", "hover", "condensed"), 
                       full_width = TRUE) {
  
  t %>%
    knitr::kable() %>%
    kableExtra::kable_styling(
      bootstrap_options = boot_opt,
      full_width = full_width
    )
}
```

For the Fitbit Collected active minutes we will make use of the **Log Entry Report** collected from [Vibrent](https://staystrong.vibrenthealth.com/#/). There are several issues to be aware of when it comes to parsing these "Objective Data". First, we have yet to combine information from **Fitbit** and **Vibrent**, where they do sometimes differ in their recording of active minute data. To get a sense of the extent of this issue see the [DifferPlots](I:\StayStrong\5. Identifiable Data (sensitive data)\Fitbit Exports\DifferPlots.pdf) document. More impactful to the results is the issue of how to then define what a Stay Strong subjects "12-month active minutes" is composed of. Any choice represents a degree of freedom on our part that will impact the shape of the measure we wish to analyze. This is one of those situations where a sensitivity analysis is warranted to examine how "robust" are choice of measure is. Myra suggested we choose the closest week to 12-months post baseline that has active minute data. I feel we should establish a range or window of about 1-month pre- and post- $t_0 + 182.5$ ($t_0 + 152.5 \leq t_6 \leq t_0 + 212.5$), so that we can find the appropriate week.

Packages in this section

```{r}
library(tidyverse) # data management tools + ggplot
library(magrittr)  # additional pipe operators: add(), and %<>%
library(readxl)    # read excel docs
```

## Baseline

We can build off of past work and start with the "cleaned" baseline database from the **Sex** Analysis project.

```{r}
drive <- "I:/StayStrong"
subdir1 <- "8. Quantitative Analysis"
subdir2 <- "Programs"
subdir3 <- "Baseline"
subdir4 <- "3b_analysis_table_one_bysex"
file <- "StayStrongBaselineBySex.rds"
path <- paste(drive, subdir1, subdir2, subdir3, subdir4, file, sep = "/")

baseline <- readRDS(path)
```

## Study-Arm

```{r}
arms <- readRDS("I:/StayStrong/8. Quantitative Analysis/Programs/ArmAndCrosswalk.rds")

dim(arms)
```

## 6-Month

We will have to join baseline with 6-month data, after first preparing 6-month data in the same way as baseline data, with regards to active minutes. Baseline active minutes were cleaned using data from the **Goals** portion of the Vibrent data, this approach will not work for subsequent Fitbit data, and will have to use the data in the **Fitbit** sheet.

### Qualtrics Survey

```{r}
subdir3 <- "6 Month"
subdir4 <- "2_survey_preparation"
file <- "6MonthDB.rds"
path <- paste(drive, subdir1, subdir2, subdir3, subdir4, file, sep = "/")
sixmo <- readRDS(path)
```

Tables in 6-Month database:

```{r}
data.frame(tables = names(sixmo)) %>% tableStyle()
```

## 12-Month

### Qualtrics Survey

```{r}
subdir3 <- "12 Month"
subdir4 <- "2_survey_preparation"
file <- "12MonthDB.rds"
path <- paste(drive, subdir1, subdir2, subdir3, subdir4, file, sep = "/")
twelvemo <- readRDS(path)
```

Tables in 12-Month database:

```{r}
data.frame(tables = names(twelvemo)) %>% tableStyle()
```

## Vibrent Data

```{r}
subdir1 <- "6. Limited Data (sensitive data)"
subdir2 <- "Vibrent Exports"
subdir3 <- "Log Entry Reports"

# Data are stored in archives
# Archive 1
file <- "Log_Entry_Report_ARCHIVE_1.xlsx"
path <- paste(drive, subdir1, subdir2, subdir3, file, sep = "/")

vibrent1 <- readxl::read_xlsx(path, sheet = "Fitbit")

# Archive 2
file <- "Log_Entry_Report_ARCHIVE_2.xlsx"
path <- paste(drive, subdir1, subdir2, subdir3, file, sep = "/")

vibrent2 <- readxl::read_xlsx(path, sheet = "Fitbit")

# Archive 3
file <- "Log_Entry_Report_ARCHIVE_3.xlsx"
path <- paste(drive, subdir1, subdir2, subdir3, file, sep = "/")

vibrent3 <- readxl::read_xlsx(path, sheet = "Fitbit")

vibrent <- rbind(vibrent1, vibrent2, vibrent3) %>% distinct()
dim(vibrent)
```

```{r, echo = FALSE, eval = TRUE}
rm(vibrent1, vibrent2, vibrent3)
```
