# ClinicalTrials.gov

Additional packages for this section

```{r}
library(emmeans)
library(lme4)
library(lmerTest)
```


Information required for the Clinical Trials analysis differs considerably from the paper, with four outcomes measured as the *Change* in outcome from baseline to 12-months post baseline. For the purposes of these analyses, the breakdown of the outcomes,

1. Primary Outcome Measures
    + Change in Physical Activity as Measured with Study-provided Monitoring Device [Time Frame: Change from Baseline in objectively monitored physical activity at one year after randomization]
2. Secondary Outcome Measures
    + Change in Weight as Measured with Study-provided scale or From Medical Record (for Missing Values) [Time Frame: Change from Baseline in weight at one year after randomization]
    + Change in Depression Score as Assessed by the personal Health Questionnaire Depression Scale (PHQ-8) [Time Frame: Change from Baseline Depression score at one year after randomization]
    + Change in Pain Measures as Assessed by the VA Pain Intensity [Time Frame: Change from Baseline in Pain measures at one year after]
    
## Primary Outcomes

### Physical Activity

Physical activity is measured as Active Minutes by a wearable Fitbit Charge 2 device; daily activity is averaged over a one week period for which at least 5 days of valid data are available.

```{r}
mod1 <- lmer(
  activeMinutes ~ measureTime * arm + Sex + baseline_goal + TypeSphone + 
    (1 | VibrentID),
  data = SSout
)

anova(mod1)
```

```{r}
emmip(mod1, arm ~ measureTime, CIs = TRUE)
```

```{r}
em1 <- emmeans(mod1, pairwise ~ measureTime | arm)

em1
confint(em1)
```

On clinical trials.gov I would report the contrasts as -67.1 (95% CI: -141.5, 7.35) and -69.0 (95% CI: -148.1, 10.18) for the SS+Coaching and SS interventions, respectively. Again, the **estimated marginal means/least squares means** are derived from a linear mixed model/rmANOVA/rmANCOVA (rm = repeated measures), adjusted for **baseline AM goal**, Type of **Smart Phone**, and **Sex**. Tests, which are not going to be reported on ClinicalTrials.gov for this study, are from a superiority study, where we would have liked to assume that SS+Coaching > SS.

As for the Method of estimation section, it's a little strange but I believe it is asking for the contrasts from an overall test,

```{r}
cont <- contrast(
  em1, 
  "consec", 
  simple = "each", 
  combine = TRUE, 
  adjust = "mvt"
)

confint(cont$contrasts)
```

Pretty wide, 1.88 (-119.0, 122.7).

So, in terms of the [ClinicalTrials.gov](https://clinicaltrials.gov/) *Statistical Analysis* Form, under the **Method of Estimation** section, we would state following:

Requested Info             | Data
-------------------------- | -----------------
Estimation Parameter       | Slope
Estimated Value            | 1.88
Confidence Interval        | 95% 2-sided (LB: -119.0, UB: 122.7)
Parameter Dispersion Type  | Standard Error of the Mean (SE)
Parameter Dispersion Value | 46.2

As for the **Estimation Comments** Section:

> Above estimate generated through repeated measures ANCOVA predicting Active Minutes as a function of arm and follow-up time, adjusted for Sex, Baseline Physical Activity Goal (Active Minutes), and type of Smart Phone. Estimate represents the contrast between SS+Coaching, 12 mos. - Baseline vs. SS alone, 12 mos. - Baseline.

How many people in each arm at each time point?

```{r, echo = FALSE, eval = TRUE}
SSout %>% 
  select(
    VibrentID, 
    arm, 
    measureTime, 
    activeMinutes, 
    baseline_goal, 
    Sex, 
    TypeSphone
  ) %>% 
  na.omit() %>%
  group_by(arm, measureTime) %>% 
  count() %>%
  tableStyle()
```

## Secondary Outcomes

### Weight

We used weight from CDW, as data from the provided scales were unreliable.

```{r}
mod2 <- lmer(
  Weight ~ measureTime * arm + (1 | VibrentID),
  data = wtDisc
)

anova(mod2)
```

```{r}
emmip(mod2, arm ~ measureTime, CIs = TRUE)
```

```{r}
em2 <- emmeans(mod2, pairwise ~ measureTime | arm)

em2
confint(em2)
```

On clinical trials.gov I would report the contrasts as -0.121 (95% CI: -7.25, 7.01) and 4.902 (95% CI: -1.65, 11.45) for the SS+Coaching and SS interventions, respectively. Again, the **estimated marginal means/least squares means** are derived from a linear model/ANOVA/ANCOVA. Tests, which are not going to be reported on ClinicalTrials.gov for this study, are from a superiority study, where we would have liked to assume that SS+Coaching > SS.

As for the Method of estimation section,

```{r}
cont <- contrast(
  em2, 
  "consec", 
  simple = "each", 
  combine = TRUE, 
  adjust = "mvt"
)

confint(cont$contrasts)
```

Pretty wide, -5.02 (-15.85, 5.81).

So, in terms of the [ClinicalTrials.gov](https://clinicaltrials.gov/) *Statistical Analysis* Form, under the **Method of Estimation** section, we would state following:

Requested Info             | Data
-------------------------- | -----------------
Estimation Parameter       | Slope
Estimated Value            | -5.02
Confidence Interval        | 95% 2-sided (LB: -15.85, UB: 5.81)
Parameter Dispersion Type  | Standard Error of the Mean (SE)
Parameter Dispersion Value | 56.7

As for the **Estimation Comments** Section:

> Above estimate generated through repeat measures ANCOVA predicting Weight as a function of the interaction of arm and follow-up time. Estimate represents the contrast between SS+Coaching, 12 mos. - Baseline vs. SS alone, 12 mos. - Baseline.

How many people in each arm at each time point?

```{r, echo = FALSE, eval = TRUE}
wtDisc %>% 
  select(
    VibrentID, 
    arm, 
    measureTime, 
    Weight
  ) %>% 
  na.omit() %>%
  group_by(arm, measureTime) %>% 
  count() %>%
  tableStyle()
```

### Depression

```{r}
depress <- SSDB$arm %>%
  select(VibrentID, arm) %>%
  left_join(
    SSDB$baseline$Survey %>%
      select(VibrentID, PHQ_score) %>%
      rename(PHQ_t0 = PHQ_score),
    by = "VibrentID"
  ) %>%
  left_join(
    SSDB$sixmo$Survey %>%
      select(VibrentID, PHQ_score) %>%
      rename(PHQ_t6 = PHQ_score),
    by = "VibrentID"
  ) %>%
  left_join(
    SSDB$twelvemo$Survey %>%
      select(VibrentID, PHQ_score) %>%
      rename(PHQ_t12 = PHQ_score),
    by = "VibrentID"
  ) %>%
  reshape2::melt(id.vars = c("VibrentID", "arm")) %>%
  rename(
    measureTime = variable,
    PHQ_score = value
  ) %>%
  mutate(
    clin_depress = ifelse(PHQ_score >= 10, 1, 0),
    clin_depress = factor(clin_depress, 0:1, c("PHQ < 10", "PHQ >= 10")),
    measureTime = gsub("PHQ_", "", measureTime),
    measureTime = factor(measureTime, 
                         c("t0", "t6", "t12"),
                         c("t0", "t6", "t12"))
  ) %>%
  na.omit()
```

We measured depression through the PHQ-8 survey, and for the purposes of the ClinicalTrials.gov analysis, we will model PHQ-8 continuously as opposed to the clinical cutoff/threshold of "10", indicating clinical depression (as measured by this scale).

```{r}
mod3 <- lmer(
  PHQ_score ~ measureTime * arm + (1 | VibrentID),
  data = depress
)

anova(mod3)
```

```{r}
emmip(mod3, arm ~ measureTime, CIs = TRUE)
```

```{r}
em3 <- emmeans(mod3, pairwise ~ measureTime | arm)

em3
confint(em3)
```

On clinical trials.gov I would report the contrasts as -0.410 (95% CI: -1.510,0.690) and 0.752 (95% CI: -0.442, 1.946) for the SS+Coaching and SS interventions, respectively. Again, the **estimated marginal means/least squares means** are derived from a linear mixed model/rmANOVA/rmANCOVA. Tests, which are not going to be reported on ClinicalTrials.gov for this study, are from a superiority study, where we would have liked to assume that SS+Coaching > SS.

As for the Method of estimation section,

```{r}
cont <- contrast(
  em3, 
  "consec", 
  simple = "each", 
  combine = TRUE, 
  adjust = "mvt"
)

confint(cont$contrasts)
```

Pretty narrow when you consider the range of the PHQ-8, -1.162 (-2.969, 0.646).

So, in terms of the [ClinicalTrials.gov](https://clinicaltrials.gov/) *Statistical Analysis* Form, under the **Method of Estimation** section, we would state following:

Requested Info             | Data
-------------------------- | -----------------
Estimation Parameter       | Slope
Estimated Value            | -1.162
Confidence Interval        | 95% 2-sided (LB: -2.969, UB: 0.646)
Parameter Dispersion Type  | Standard Error of the Mean (SE)
Parameter Dispersion Value | 0.690

As for the **Estimation Comments** Section:

> Above estimate generated through ANCOVA predicting PHQ-8 Score as a function of the interaction of arm and follow-up time. Estimate represents the contrast between SS+Coaching, 12 mos. - Baseline vs. SS alone, 12 mos. - Baseline.

How many people in each arm at each time point?

```{r, echo = FALSE, eval = TRUE}
depress %>% 
  select(
    VibrentID, 
    arm, 
    measureTime, 
    PHQ_score
  ) %>% 
  na.omit() %>%
  group_by(arm, measureTime) %>% 
  count() %>%
  tableStyle()
```

### Pain

```{r}
pain <- SSDB$arm %>%
  select(VibrentID, arm) %>%
  left_join(
    SSDB$baseline$Survey %>%
      select(VibrentID, PainPastWeek) %>%
      rename(Pain_t0 = PainPastWeek),
    by = "VibrentID"
  ) %>%
  left_join(
    SSDB$sixmo$Survey %>%
      select(VibrentID, PainPastWeek) %>%
      rename(Pain_t6 = PainPastWeek),
    by = "VibrentID"
  ) %>%
  left_join(
    SSDB$twelvemo$Survey %>%
      select(VibrentID, PainPastWeek) %>%
      rename(Pain_t12 = PainPastWeek),
    by = "VibrentID"
  ) %>%
  reshape2::melt(id.vars = c("VibrentID", "arm")) %>%
  rename(
    measureTime = variable,
    PainPastWeek = value
  ) %>%
  mutate(
    clin_sig_pain = ifelse(PainPastWeek >= 4, 1, 0),
    clin_sig_pain = factor(clin_sig_pain, 0:1, c("Pain < 4", "Pain >= 4")),
    measureTime = gsub("Pain_", "", measureTime),
    measureTime = factor(measureTime, 
                         c("t0", "t6", "t12"),
                         c("t0", "t6", "t12"))
  ) %>%
  na.omit()
```

Neuropathic pain is measured on an 11 point scale (0-10), administered via survey at each follow-up time-point. Similar to Depression, we will use the continuous scale for estimation as opposed to the clinical cut-off of "4" indicating clinically significant pain.

```{r}
mod4 <- lmer(
  PainPastWeek ~ measureTime * arm + (1 | VibrentID),
  data = pain
)

anova(mod4)
```

```{r}
emmip(mod4, arm ~ measureTime, CIs = TRUE)
```

```{r}
em4 <- emmeans(mod4, pairwise ~ measureTime | arm)

em4
confint(em4)
```

On clinical trials.gov I would report the contrasts as 0.212 (95% CI: -0.2145, 0.639) and 0.557 (95% CI: 0.0968, 1.018) for the SS+Coaching and SS alone interventions, respectively. Again, the **estimated marginal means/least squares means** are derived from a linear mixed model/rmANOVA/rmANCOVA. Tests, which are not going to be reported on ClinicalTrials.gov for this study, are from a superiority study, where we would have liked to assume that SS+Coaching > SS.

As for the Method of estimation section,

```{r}
cont <- contrast(
  em4, 
  "consec", 
  simple = "each", 
  combine = TRUE, 
  adjust = "mvt"
)

confint(cont$contrasts)
```

Pretty narrow when you consider the range of the 0-10, -0.3454 (-1.044, 0.35359).

So, in terms of the [ClinicalTrials.gov](https://clinicaltrials.gov/) *Statistical Analysis* Form, under the **Method of Estimation** section, we would state following:

Requested Info             | Data
-------------------------- | ------------------------------------
Estimation Parameter       | Slope
Estimated Value            | -0.3454
Confidence Interval        | 95% 2-sided (LB: -1.044, UB: 0.353)
Parameter Dispersion Type  | Standard Error of the Mean (SE)
Parameter Dispersion Value | 0.267

As for the **Estimation Comments** Section:

> Above estimate generated through ANCOVA predicting "Pain In Past Week" as a function of the interaction of arm and follow-up time. Estimate represents the contrast between SS+Coaching, 12 mos. - Baseline vs. SS alone, 12 mos. - Baseline.

How many people in each arm at each time point?

```{r, echo = FALSE, eval = TRUE}
pain %>%
  select(
    VibrentID,
    arm,
    measureTime,
    PainPastWeek
  ) %>%
  na.omit() %>%
  group_by(arm, measureTime) %>%
  count() %>%
  tableStyle()
```
